\vspace{1.0cm} \LARGE \bf fluB

### 2013-05-26 fluB.tex
Trying to get this to work properly :D.
This should work. All the stuff that's been done so far going up on
github. Very provisional so far.
Adding line breaks after sentences.

As members of \textit{Orthomyxoviridae}, all influenza viruses have segmented genomes, which allow viruses co-infecting the same cell to exchange segments (a process known as reassortment). Influenza A viruses are widely considered to be a major threat to human health worldwide due to the ability to cause pandemics in humans via reassortment of seasonal human and non-human influenza A strains. The only known persistent source of influenza B viruses are humans (and occasionaly seals \cite{osterhaus2000}) and thus the antigenic diversity of influenza B viruses is considered to be low. It has been suggested that influenza B viruses use a combination of reassortment and amino acid insertion-deletion to generate antigenic novelty.

>>>>

As members of \textit{Orthomyxoviridae}, all influenza viruses have segmented genomes, which allow viruses co-infecting the same cell to exchange segments (a process known as reassortment). 
Influenza A viruses are widely considered to be a major threat to human health worldwide due to the ability to cause pandemics in humans via reassortment of seasonal human and non-human influenza A strains. 
The only known persistent source of influenza B viruses are humans (and occasionaly seals \cite{osterhaus2000}) and thus the antigenic diversity of influenza B viruses is considered to be low. 
It has been suggested that influenza B viruses use a combination of reassortment and amino acid insertion-deletion to generate antigenic novelty (comment - citation).
